Squint: Lossy Hierarchical Compression on Symbol Streams

### 2012-12-10 tex/paper.tex
some bullet points for conclusions

In this paper we develop 2 algorithms and implement a system for lossily
compressing text while preserving its hierarchical structures. The goal
was to preserve the feel of a text at both micro and macro levels. 
Since grammar-based compression schemes were designed to capture
these structures, we built
our system on top of the existing \Sequitur grammar inference algorithm. 
Starting with the CFG generated by a lossless grammar
inference algorithm, we repeatedly simplify it, throwing out details
along the way to emphasize repetitions. Our main contribution lies in the
development of 2 algorithms for ``simplifying'' CFG grammars while 
preserving their structure.

@@

\subsection{Larger Tests}
Genesis-256000
Obfuscated C Code

\section{Conclusions}
\subsection{Algorithm Tradeoffs}
Runtimes for each algorithm
Considerations in choosing epsilon
\subsection{Ratios and Fidelity}
\subsection{Future Work}
* Better ways to set epsilon to maximize value / cost for different size and types
* Better ways to quantify preservation of hierarchies
* How to find near `self-similarities' that aren't captured by a rule
* Iterating lossify and reduce in a cycle

>>>>

In this paper we develop 2 algorithms and implement a system for lossily
compressing text while preserving its hierarchical structures. The goal
was to preserve the feel of a text at both micro and macro levels. 
Since grammar-based compression schemes were designed to capture
these structures, we built
Music Final Composition: Dec 10
our system on top of the existing \Sequitur grammar inference algorithm. 
Starting with the CFG generated by a lossless grammar
inference algorithm, we repeatedly simplify it, throwing out details
along the way to emphasize repetitions. Our main contribution lies in the
development of 2 algorithms for ``simplifying'' CFG grammars while 
preserving their structure.

@@

\subsection{Larger Tests}
Genesis-256000
Obfuscated C Code (looks really cool!)

\section{Conclusions}
\subsection{Summary of Results}
* General concept of simplifying grammars, two proposed algorithms
* reasonably efficient implementation with runtime better than expected
* compared algorithms, evaluated effectiveness of reducer
* looked at effect of epsilon

\subsection{Ratios and Fidelity}

* How useful are these algorithms??
* What is the ratio we get
* What kind of fidelity to we get

\subsection{Future Work}
* Better ways to set epsilon to maximize value / cost for different size and types
* Better ways to quantify preservation of hierarchies
* How to find near `self-similarities' that aren't captured by a rule
* Iterating lossify and reduce in a cycle
